\documentclass[../thesis.tex]{subfiles}

\begin{document}

First and foremost, I would like to thank my parents, Amy and Steve, for their unconditional support of my educational aspirations and passionate cultivation of my curiosities in addition to their persistent emotional, financial, and logistical aid they have provided during my long journey up till this point.  Also, I would like to thank my siblings, Maggie, Lucy, and Charlie, for their friendship and inspiration, as well as the examples they set which I was able to follow.  Moreover, I would like to thank my grandparents, aunts, uncles and cousins for their words of encouragement and praise.  Lastly, I would like to thank my friends in East Lansing, Illinois, and around the country for helping me have fun and maintain my peace of mind, and never failing to ask me when I would graduate.

Next, I would like to thank my all my teachers throughout my long tenure as a student.  I would especially like to acknowledge my science and math teachers that fostered and encouraged my interests.  In particular, I would like to credit Bryon Leonard for opening my mind to the beauty of modern physics and the path that leads to where I am now.  Additionally, I am thankful for Philippe Collon and Michael Thoennessen for giving me my first research opportunities as an undergraduate student when I'm sure I was more of a burden than a blessing.

I am grateful to Dr. Georg Bollen and Dr. Ryan Ringle for inviting me into the LEBIT collaboration, my first academic family.  Along with my fellow graduate students, David Lincoln, Scott Bustabad, and Brad Barquest, my LEBIT colleagues helped me find my place as a graduate student, guided me as a scientist and collaborator, provided opportunities to travel and present at national conferences, and gave me research experience that few theorists hold.  While in LEBIT, I was fortunate to share an office with Jenna Smith, who looked over me as a young graduate student and gave me valuable advice and encouragement when it was greatly needed.

When I mentioned that I decided to change my research direction, my current advisor, Morten Hjorth-Jensen, without hesitation and without any solicitation from me, took a risk by taking me on as a student.  For this, I am eternally grateful, and because Morten has become an invaluable mentor, colleague, and friend, I feel very lucky for finding myself in that situation.  Along with my advisor, I would like to thank the members of my committee--Scott Bogner, Piotr Piecuch, Carlo Piermarocchi, and Remco Zegers--for agreeing to join my adventure through graduate school and guiding me along the way.  I'm also indebted to Heiko Hergert for fielding my relentless questions, Ragnar Stroberg for unknowingly helping with his clean and well-commented code, and Kim Crosslan for shouldering most of my blunders for more than 7 years and for making sure I was aware of them.

Lasly, I would like to thank my fellow graduate students.  To Justin Lietz, my office mate, world traveling partner, coupled-cluster colleague, and friend, I'm thankful for lending his advice, his expertise, and his ear.  To Nathan Parzchuowki, Titus Morris, and Fei Yuan, my fellow nuclear theory colleagues and friends, I'm thankful for their constant help and the pleasant work environment that they created.

And to all of the people that I haven't mentioned, I realize that I am just a product of the circumstances that unfolded around me, especially the people with which I've crossed paths.  So I'd like to give thanks to everyone, and to no one in particular, who helped shape my success in completing this dissertation.

\end{document}
